# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
```{r echo=TRUE}
amd <- read.table("activity.csv", header=TRUE, sep=",", na.strings="NA")
amd$date <- as.Date(amd$date)
```

## What is mean total number of steps taken per day?
- Make a histogram of the total number of steps taken each day
```{r echo=TRUE}
library(ggplot2)
attach(amd)
qplot(date, steps, geom="bar", stat="identity")
detach(amd)
```
- Calculate and report the mean and median total number of steps taken per day
```{r echo=TRUE}
library(sqldf)
final<-amd[complete.cases(amd$steps),]
newtab <- sqldf("select sum(steps) as sum_steps, avg(steps) as avg_steps, date from final group by date")
newtab
```

## What is the average daily activity pattern?
- Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r echo=TRUE}
dap <- sqldf("select avg(steps) as avg_int_steps, interval from final group by interval")
plot(dap$interval, dap$avg_int_steps, type="l", xlab="5-minute interval", ylab="Average number of steps taken")
```
-Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r echo=TRUE}
max(dap$avg_int_steps)
```

## Imputing missing values
- Calculate and report the total number of missing values in the dataset 
```{r echo=TRUE}
sum(!complete.cases(amd$steps))
```
- Devise a strategy for filling in all of the missing values in the dataset. 
- Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r echo=TRUE}
line <- nrow(amd)
length <- nrow(dap)
for (i in 1:line){
        if (is.na(amd$steps[i])){
                for (j in 1:length){
                        if (amd$interval[i]==dap$interval[j])
                                break
                }
                amd$steps[i] <- dap[j,1]
        }
}
newamd <- amd
amd <- read.table("activity.csv", header=TRUE, sep=",", na.strings="NA")
```
- Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day.
```{r}
attach(newamd)
qplot(date, steps, geom="bar", stat="identity")
detach(newamd)
newtab2 <- sqldf("select sum(steps) as sum_steps, avg(steps) as avg_steps, date from newamd group by date")
newtab2
```

## Are there differences in activity patterns between weekdays and weekends?
-Create a new factor variable in the dataset.
```{r}
newamd <- transform(newamd, date = weekdays(as.Date(newamd$date, "%Y-%m-%d")))
long <- nrow(newamd)
for (x in 1:long){
        if(newamd$date[x]=="星期日"){
                newamd$date[x]<-"Weekend"
        }else if(newamd$date[x]=="星期六"){
                newamd$date[x]<-"Weekend"
        }else
                newamd$date[x]<-"Weekday"
}
amdweekend <- subset(newamd, date=="Weekend", select=steps:interval)
amdweekday <- subset(newamd, date=="Weekday", select=steps:interval)
newweekend <- sqldf("select avg(steps) as avg_steps, interval, date from amdweekend group by interval")
newweekday <- sqldf("select avg(steps) as avg_steps, interval, date from amdweekday group by interval")
newamd <- rbind(newweekend, newweekday)
library(lattice)
xyplot(avg_steps ~ interval|date,type="l",data = newamd, layout = c(1, 2), xlab="Interval", ylab="Number of steps")
```

